\documentclass[11pt,a4paper]{article}
\usepackage[margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{hyperref}
\usepackage{longtable}
\usepackage{array}
\usepackage{enumitem}
\setlist[itemize]{leftmargin=1.5em}
\setlist[enumerate]{leftmargin=1.8em}
\hypersetup{
  colorlinks=true,
  linkcolor=black,
  urlcolor=blue,
  pdftitle={Complaint Management System User Manual},
  pdfauthor={Complaint Management Team}
}

\title{Complaint Management System\\User Manual}
\author{Complaint Management Team}
\date{April 17, 2026}

\begin{document}
\maketitle
\tableofcontents
\newpage

\section{Scope Clarification}
The interface references Discord and GitHub complaint sources, but direct external platform integrations are not implemented in this release.

This is intentional and consistent with the original project scope: Discord/GitHub connector integrations were not part of the SRS.

\section{Purpose}
This manual explains how to use the Complaint Management System dashboard for day-to-day complaint triage and tracking.

The app is intended for maintainers who need to:
\begin{itemize}
  \item review incoming complaints from Discord,
  \item promote valid complaints into active work,
  \item track active work on a Kanban board,
  \item inspect details in a side drawer,
  \item create new complaints directly.
\end{itemize}

\section{Prerequisites and Startup}
Required:
\begin{itemize}
  \item Node.js and npm
  \item Docker
\end{itemize}

From the project root:
\begin{verbatim}
npm install
cp .env.example .env
npm run setup
npm run dev
\end{verbatim}

Open:
\begin{itemize}
  \item \url{http://localhost:3000}
\end{itemize}

The home route redirects to \texttt{/dashboard/triage}.

\section{Dashboard Layout}
The UI has four primary areas:
\begin{enumerate}
  \item Sidebar (left): navigation, triage count, saved filters, collapse control.
  \item Top bar: command palette trigger and New Complaint action.
  \item Main content: Triage, Board, or Settings.
  \item Overlays: Issue Drawer, Create Complaint modal, Command palette.
\end{enumerate}

\section{Navigation}
\subsection{Triage Inbox}
Path: \texttt{/dashboard/triage}

Used to review incoming Discord complaints before promotion.

Filters:
\begin{itemize}
  \item Pending
  \item All
  \item Flagged Duplicate
  \item Promoted
  \item Spam
\end{itemize}

\subsection{Active Board}
Path: \texttt{/dashboard/board}

Used to track active work through stages:
\begin{itemize}
  \item Backlog
  \item Todo
  \item In Progress
  \item In Review
  \item Done
\end{itemize}

\subsection{Settings}
Path: \texttt{/dashboard/settings}

Settings cards are currently informational placeholders for future phases.

\section{Triage Inbox Workflow}
\subsection{Inspect complaints}
Each row includes complaint number, title, labels, similarity score, reporter, age, status, and quick actions.
Click a row to open the Issue Drawer.

\subsection{Promote to board}
Promote via:
\begin{itemize}
  \item row hover action,
  \item key \texttt{p} on focused row,
  \item command palette action,
  \item drawer footer button.
\end{itemize}

Result: status moves to \texttt{BACKLOG}, item appears on Active Board.

\subsection{Mark spam}
Mark spam via row hover action, key \texttt{x}, command palette, or drawer footer.

Result: status moves to \texttt{TRIAGE\_SPAM}.

\subsection{Mark done}
Use key \texttt{e} or command palette action.

Result: status moves to \texttt{DONE}.

\subsection{Bulk actions}
When at least two rows are selected, the bulk action bar appears.

Working bulk actions:
\begin{itemize}
  \item Promote All
  \item Spam All
  \item Clear Selection
\end{itemize}

Placeholder actions (phase-2 style feedback only):
\begin{itemize}
  \item Mass Reply and Close
  \item Assign
  \item Label
\end{itemize}

\section{Active Board Workflow}
\subsection{Move cards}
Drag a card from one column to another.

The UI updates optimistically, then persists the status on the server.

\subsection{Read card metadata}
Cards show complaint number, priority marker, labels, optional linked PR/CI status, and assignee avatars.

Click a card to open the Issue Drawer.

\subsection{Milestone progress}
If a milestone is available, header shows title, closed/total count, and a progress bar.

\section{Issue Drawer Workflow}
\subsection{Open and close}
Open from triage rows, board cards, or key \texttt{Enter} on focused triage row.

Close with \texttt{Esc}, close icon, backdrop click, or footer Close.

\subsection{View content}
Drawer may include:
\begin{itemize}
  \item title, number, status, stale marker,
  \item labels and priority,
  \item Discord thread context (Discord-source complaints),
  \item issue description (GitHub-source complaints),
  \item AI similarity section,
  \item internal notes and public replies tabs,
  \item right-side metadata: assignees, labels, milestone, GitHub links.
\end{itemize}

\subsection{Focus mode}
Toggle with key \texttt{f} or focus button in drawer header.

\subsection{Drawer actions}
Working actions:
\begin{itemize}
  \item Promote to GitHub (footer)
  \item Mark Spam (footer)
\end{itemize}

Currently shown as coming soon:
\begin{itemize}
  \item Merge into
  \item Flag Duplicate
  \item Create Branch
  \item Note compose persistence from textarea submit
\end{itemize}

\section{Create New Complaint}
Open modal via New Complaint button or key \texttt{c}.

Fields:
\begin{itemize}
  \item Title (required)
  \item Description
  \item Priority
\end{itemize}

Submit with button or \texttt{Ctrl+Enter} (or \texttt{Cmd+Enter} on macOS).

Result: complaint is created with source \texttt{GITHUB} and initial status \texttt{TODO}, then user is routed to Active Board.

\section{Command Palette}
Open with \texttt{Ctrl+K} (or \texttt{Cmd+K}) or top-bar trigger.

Groups:
\begin{itemize}
  \item Navigate: triage, board, settings
  \item Actions: assign, promote, spam, done, merge, flag duplicate
  \item View: toggle focus mode
\end{itemize}

Some actions are placeholders depending on implementation state.

\section{Keyboard Shortcuts}
\begin{longtable}{>{\raggedright\arraybackslash}p{0.30\textwidth} >{\raggedright\arraybackslash}p{0.62\textwidth}}
\textbf{Shortcut} & \textbf{Effect} \\
\hline
\texttt{c} & Open Create Complaint modal \\
\texttt{Esc} & Close drawer or create modal \\
\texttt{Ctrl+K} / \texttt{Cmd+K} & Open command palette \\
\texttt{?} & Toggle keyboard help event \\
\texttt{f} & Toggle drawer focus mode \\
\texttt{j} / \texttt{k} & Move triage focus down/up \\
\texttt{Enter} & Open focused triage complaint \\
\texttt{p} & Promote focused complaint \\
\texttt{x} & Mark focused complaint as spam \\
\texttt{e} & Mark focused complaint done \\
\texttt{a} & Assign-to-me event (placeholder) \\
\texttt{m} & Merge event (placeholder) \\
\texttt{g} then \texttt{t} & Go to Triage \\
\texttt{g} then \texttt{b} & Go to Board \\
\texttt{g} then \texttt{s} & Go to Settings \\
\end{longtable}

\section{Status Reference}
\begin{itemize}
  \item \texttt{TRIAGE\_PENDING}: New triage complaint
  \item \texttt{TRIAGE\_SPAM}: Triage complaint marked as spam
  \item \texttt{TRIAGE\_PROMOTED}: Exists in model (current promote flow sets \texttt{BACKLOG})
  \item \texttt{BACKLOG}: Board backlog
  \item \texttt{TODO}: Ready for implementation
  \item \texttt{IN\_PROGRESS}: Active work
  \item \texttt{IN\_REVIEW}: Under review
  \item \texttt{DONE}: Completed
  \item \texttt{CLOSED}: Closed/duplicate terminal state
\end{itemize}

\section{Implemented vs Placeholder}
Implemented and persisted:
\begin{itemize}
  \item triage promote, spam, done,
  \item bulk promote and bulk spam,
  \item board drag-and-drop status updates,
  \item complaint creation,
  \item drawer data loading.
\end{itemize}

Placeholder/phase-2 style interactions:
\begin{itemize}
  \item settings cards,
  \item merge and duplicate-flag actions,
  \item assign-to-me keyboard/command behavior,
  \item note submission from textareas.
\end{itemize}

\section{Troubleshooting}
\subsection*{App or DB errors}
Ensure Docker is running, then execute:
\begin{verbatim}
npm run db:up
npm run db:push
npm run db:seed
\end{verbatim}

\subsection*{No demo data visible}
Reseed:
\begin{verbatim}
npm run db:seed
\end{verbatim}

\subsection*{Port 5432 conflict}
Stop conflicting PostgreSQL service or update database configuration.

\subsection*{UI appears stale}
Hard refresh browser and retry action.

\section{Suggested Daily Workflow}
\begin{enumerate}
  \item Start in Triage Inbox for pending and critical complaints.
  \item Promote valid complaints to board.
  \item Mark clear spam quickly.
  \item Drive active work across board columns.
  \item Open drawer for context before major state changes.
  \item Create direct internal complaints via modal when needed.
\end{enumerate}

\end{document}
